### 2019-05-02 sections/language.tex
rename Calculus -> Language
lambda -> \lambda
remove reference to deleted figure

\section{Calculus}
\label{sec:language}

@@

\label{sub:expressions}
The host language is a simply typed $lambda$-calculus, extended with some basic types and \ML-style references.
We use references to represent shared data sources.
The grammar in \cref{fig:language-grammar} defines the syntax of the host language.
It has abstractions, applications, variables, and constants for booleans, integers and strings.
The symbol $\star$ stands for binary operators.
For the result of parallel tasks we need pairs.
Conditionals come in handy for defining guards.
%
References will be used to implement shared editors.
Our treatment of references closely follows the one by \citet{books/Pierce02TAPL}.
Creating a reference using the keyword $\Ref$ yields a location $l$.
While $x$ denotes program variables, $l$ denotes store locations.
Locations are not intended to be directly manipulated by the programmer.
The symbols ! and $:=$ stand for dereferencing and assignment.
The unit value will be used as the result of assignments.

@@

Programs in \TOPHAT model interactive workflows.
Interaction means communication with end users.
End users should be able to enter information into the system, change it, clear it, reenter it, and so on.
To do this, we introduce the concept of \emph{editors}.
%
Editors are typed containers that either hold a value or are empty.
Editors that have a value can be \emph{changed} or \emph{emptied}.
Empty editors can be \emph{filled}.
This is depicted as a state diagram in \cref{fig:editor-state} below.

>>>>

\section{Language}
\label{sec:language}

@@

\label{sub:expressions}
The host language is a simply typed $\lambda$-calculus, extended with some basic types and \ML-style references.
We use references to represent shared data sources.
The grammar in \cref{fig:language-grammar} defines the syntax of the host language.
It has abstractions, applications, variables, and constants for booleans, integers and strings.
The symbol $\star$ stands for binary operators.
For the result of parallel tasks we need pairs.
Conditionals come in handy for defining guards.
%
References will be used to implement shared editors.
Our treatment of references closely follows the one by \citet{books/Pierce02TAPL}.
Creating a reference using the keyword $\Ref$ yields a location $l$.
While $x$ denotes program variables, $l$ denotes store locations.
Locations are not intended to be directly manipulated by the programmer.
The symbols ! and $:=$ stand for dereferencing and assignment.
The unit value will be used as the result of assignments.

@@

Programs in \TOPHAT model interactive workflows.
Interaction means communication with end users.
End users should be able to enter information into the system, change it, clear it, reenter it, and so on.
To do this, we introduce the concept of \emph{editors}.
%
Editors are typed containers that either hold a value or are empty.
Editors that have a value can be \emph{changed} or \emph{emptied}.
Empty editors can be \emph{filled}.
